Stimulated Accretion from Circumgalactic Media Interactions

### 2024-02-15 paper/ms.tex
Adding dilution profile just to have in history

>>>>

\subsection{Dilution Profile}\label{ssec:dilprof}

Hi. We next examine the constitution of gas in the disk at $t=5\,\textrm{Gyr}$, i.e.
post-merger when the disk has settled. We compute the ``dilution fraction'' --
the fraction of gas in a given annulus in the disk ($|z|<3\,\textrm{kpc}$) that
originated from GSE or its CGM, and show this in the upper panel of
Figure~\ref{fig:dil}. The dilution factor varies from $\sim10\%$ in the inner
disk to only a few percent in the outer disk. In fact, of all GSE gas with
$R<15\,\textrm{kpc}$, $x\%$ is within $y$.

In the bottom panel of Figure~\ref{fig:dil}, we attempt to illustrate how much
the dilution of the disk impacts its metallicity. We assign the gas in the disk
which was originally part of the Milky Way disk and CGM a metallicity of
$[\textrm{Z}/\textrm{H}]=-0.3$ and the gas from the GSE disk and CGM a
metallicity of $[\textrm{Z}/\textrm{H}]=-1.2$. We compute the metallicity of
each annulus assuming these two gas components are well mixed.\footnote{Only
about $1\%$ of cells in the disk contain tracer particles only from GSE.}
Because there is little dilution in the outer disk, the metallicity hardly
changes from $-0.3$. In the inner disk where dilution is stronger, the
metallicity drops to $\sim-0.35$. We also plot horizontal dashed lines at the
assumed metallicity of Milky Way gas ($-0.3$) and the approximate metallicity of
the start of the low-alpha sequence ($-0.6$), i.e. the target metallicity of the
GSE merger.

% 1% number is in dilution_profile notebook

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{dil.pdf}
  \caption{The dilution and metallicity profiles of the disk resulting from the
  merger between the Milky Way and GSE. The upper panel shows the ``dilution
  fraction'' -- the fraction of gas at each annulus originating from the disk or
  CGM of GSE. The lower panel shows the metallicity profile of the disk,
  assuming metallicities of $[\textrm{Z}/\textrm{H}]=-0.3$ and $-1.2$ for gas
  from the Milky Way and GSE, respectively. The dashed lines at
  $[\textrm{Z}/\textrm{H}]=-0.3$ and $-0.6$ are the approximate metallicites of
  the end of the high-alpha and the beginning of the low-alpha sequences. The
  disk is defined as having $|z|<3\,\textrm{kpc}$.}
  \label{fig:dil}
\end{figure}
